
---
title: "Germany 2021 Enterprise Survey - Final Analysis"
author: "Praharsha Gangadhara"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

## 1. Introduction

This project explores the Germany 2021 Enterprise Survey dataset to uncover business insights post-COVID, especially focusing on digital adoption, infrastructure, and firm performance. We utilize techniques learned throughout the course such as data cleaning, summarization, and visualization.

## 2. Loading Libraries and Data

```{r}
library(tidyverse)
library(readr)
library(ggplot2)
library(dplyr)
library(knitr)
library(caret)
library(cluster)
library(factoextra)
library(rpart)
library(rpart.plot)

# Load data
data <- read_csv("C:/Users/praha/Downloads/Germany_2021_ES.csv")
glimpse(data)
```

## 3. Data Cleaning and Preparation

We first examine missing values, select relevant variables, and prepare data for analysis.

```{r}
# Check missing data
missing_summary <- colSums(is.na(data))
missing_summary[missing_summary > 0]

# Select relevant columns for analysis
analysis_data <- data %>%
  select(id, COVc4a, c6, c7, c8a, c8b, d2, EUd1c, f1, l1) %>%
  rename(
    online_business = COVc4a,
    power_outage = c6,
    outage_count = c7,
    outage_hours = c8a,
    outage_minutes = c8b,
    annual_sales = d2,
    online_sales_pct = EUd1c,
    capacity_util = f1,
    fulltime_workers = l1
  )
```

## 4. Exploratory Data Analysis (EDA)

### 4.1 Digital Adoption Due to COVID-19

```{r}
analysis_data %>%
  count(online_business) %>%
  mutate(Response = recode(online_business, `1` = "Yes", `2` = "No", `-9` = "Don't know")) %>%
  ggplot(aes(x = Response, y = n, fill = Response)) +
  geom_col() +
  labs(title = "Digital Adoption Due to COVID-19", x = "Response", y = "Number of Firms")
```

### 4.2 Power Outage Frequency

```{r}
analysis_data %>%
  filter(!is.na(power_outage)) %>%
  count(power_outage) %>%
  mutate(PowerOutage = recode(power_outage, `1` = "Yes", `2` = "No", `-9` = "Don't know")) %>%
  ggplot(aes(x = PowerOutage, y = n, fill = PowerOutage)) +
  geom_col() +
  labs(title = "Firms Experiencing Power Outages", x = "Response", y = "Number of Firms")
```

## 5. Relationship Analysis

### 5.1 Sales vs. Online Activity

```{r}
ggplot(analysis_data, aes(x = as.factor(online_business), y = annual_sales)) +
  geom_boxplot() +
  labs(title = "Annual Sales vs. Online Activity", x = "Online Business Due to COVID", y = "Annual Sales (EUR)")
```

### 5.2 Capacity Utilization vs. Power Outages

```{r}
ggplot(analysis_data, aes(x = as.factor(power_outage), y = capacity_util)) +
  geom_boxplot() +
  labs(title = "Capacity Utilization vs. Power Outages", x = "Power Outage Experience", y = "Capacity Utilization (%)")
```

#6. Logistic Regression: Predictors of Online Adoption

```{r}
# Recode target variable to 0/1
analysis_data$online_business <- ifelse(analysis_data$online_business %in% c("Yes", "yes", "Adopted", "1"), 1, 0)

logit_model <- glm(online_business ~ power_outage + outage_count + outage_hours +
                   annual_sales + online_sales_pct + capacity_util + fulltime_workers,
                   data = analysis_data,
                   family = binomial)

summary(logit_model)
```

## 7. Clustering: Firms Based on Adoption, Sales, Outages

```{r}
cluster_data <- analysis_data %>%
  select(annual_sales, outage_count, online_sales_pct) %>%
  drop_na() %>%
  scale()

# Elbow method for k
fviz_nbclust(cluster_data, kmeans, method = "wss")

# K-means clustering
set.seed(123)
km <- kmeans(cluster_data, centers = 3, nstart = 25)

# Cluster plot
fviz_cluster(km, data = cluster_data)
```


